\documentclass[11pt,answers]{exam}

\usepackage{etex}
\usepackage{amssymb,amsmath,multicol} %<-- InWorksheetExam1 i also have fancyhdr,

\usepackage[metapost]{mfpic}
\usepackage[pdftex]{graphicx}
\usepackage{tabu}

\usepackage{pst-plot}
\usepackage{pgfplots}
\pgfplotsset{compat=1.9}

\usepackage{tikz}
\usepackage{tkz-2d}
\usepackage{tkz-base}
\usetikzlibrary{calc}
\usetikzlibrary{arrows}

\usepackage{systeme}

\usepackage[inline]{enumitem}
\usepackage{refcount}%<-- non in WorksheetExam1

\usepackage{pstricks-add,pst-eucl}
\usepackage{systeme}
\usepackage{setspace}

\def\f{x+1} \def\g{-x/3+2}  \def\h{-x+3}

\newcommand{\vasymptote}[2][]{
    \draw [densely dashed,#1] ({rel axis cs:0,0} -| {axis cs:#2,0}) -- ({rel axis cs:0,1} -| {axis cs:#2,0});
}

\addpoints
%\printanswers
\noprintanswers

\opengraphsfile{Q2a_Sp18}

\begin{document}
\extrawidth{-0.3in}
\pagestyle{headandfoot}

\setlength{\hoffset}{-.25in}

\extraheadheight{-.3in}
\runningheadrule
\firstpageheader{\bfseries {Precalculus}}{ \bfseries {Quiz 2 }}{\bfseries {9/18/18}} 

\begin{center}
	This quiz has \numquestions\ questions, for a total of \numpoints\
	points and \numbonuspoints\ bonus points.
\end{center}


\firstpagefooter{} %%&&CHANGED
                {}
                {%Points earned: \hbox to 0.5in{\hrulefill}
                % out of  \pointsonpage{\thepage} points
                }
                 
						

\vspace*{0.1cm}
\hbox to \textwidth { \scshape {Name:} \enspace\hrulefill}
\vspace{0.1in}




\pointpoints{point}{points}

\begin{questions}


\addpoints

\question The function $f(t)=4.5t+28$ gives the water level $f(t)$ (in feet) in a reservoir $t$ years after a dam was built.  

\begin{parts}

\part[1] Describe the meaning of the statement: $f(1)=32.5$  in practical terms.

\fillwithdottedlines{1cm}
\part[1] Which of the following statements best describes the meaning of the number 4.5  in practical terms?

		\begin{choices}
			\choice It is the slope;
\choice It is the change in $y$ over the change in $x$;
\choice  It is rise over run;
\choice Every year, the water level changes by 4.5 feet;
\choice Every year, the water level increases by 4.5 feet.
\end{choices}
\end{parts}

\question In a certain state the maximum speed permitted on freeways is 65 mi/h, and the minimum is 40 mi/h. The fine $F$ for violating these limits is \$40 for every mile above the maximum or below the minimum. Assume that  $x$ is the speed (in mi/h) at which you are driving.

\begin{parts}
	
	\part[2] \label{part:one} Find $F(60)$ and explain how You arrived at Your answer.
	
	\fillwithdottedlines{1.5cm}
	
		\part[2] \label {part:two} Find $F(30)$ and explain how You arrived at Your answer.
		
		\fillwithdottedlines{1.5cm}
		
		\part[2] What do your answers in Parts (\ref{part:one}) and (\ref{part:two}) mean? Please circle the best answer among the options listed below.
		
		\begin{choices}
			\choice The awards for obeying the speed limits on the freeway.
			\choice The fines for violating the speed limits on the freeway.    
			\choice The initial speed at which a fine will be incurred.
			\choice The minimum speed one can drive without paying a fine.
			\choice The maximum speed one can drive without paying a fine.
			\end{choices}
			\end{parts}

	\bonusquestion[2] Consider the function $T(x)$ measuring the thickness $T$ (in millimeters) of the eggshell of a bird as a function of the
	concentration $x$ (in parts per million, or ppm) of the pesticide DDE in the water of the environment where the bird lives.  What is the meaning of the
	statement $T(200) = 0.18$ in practical terms? Please note that Your answer should include units (ppm and millimeters).
	
	\fillwithdottedlines{1.5cm}
	




\end{questions}

\end{document}                 